Untitled

### 2020-10-25 manuscript/manuscript.Rmd
Final analysis on full data

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
run_everything = TRUE
source("../model_accuracy.R")
```

@@

```{r}
p <- PartialDependence(final, vars = ordered_vars, output = "list", rawdata = TRUE)
source("../get_signs.R")
the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

@@

>>>>

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
run_everything = FALSE
source("../model_accuracy.R")
get_signs <- function(pdps){
  sapply(pdps, function(x){
    thisvar <- x$data
    out <- table(sign(c(-1, 0, 1, diff(thisvar$preds))))-1
    if(any(out[c(1,3)] == 0) & !all(out[c(1,3)] == 0)){
      out <- c(out, c("Negative monotonous", "Positive monotonous")[which(!out[c(1,3)] == 0)])
    } else {
      if(!out[1] == out[3]){
        out <- c(out, c("Mostly negative", "Mostly positive")[(out[1] < out[3])+1])
      } else {
        out <- c(out, "Other")
      }
    }
    dif_amount <- tapply(c(0,0,0, diff(thisvar$preds)), c(-1, 0, 1, sign(diff(thisvar$preds))), sum)
    if(any(dif_amount[c(1,3)] == 0) & !all(dif_amount[c(1,3)] == 0)){
      dif_amount <- c(dif_amount, c("Negative monotonous", "Positive monotonous")[which(!dif_amount[c(1,3)] == 0)])
    } else {
      if(abs(dif_amount[3]+.00001) / abs(dif_amount[1]+.00001) > 3){
        dif_amount <- c(dif_amount, "Mostly positive")
      } else {
        if(abs(dif_amount[1]+.00001) / abs(dif_amount[3]+.00001) > 3){
          dif_amount <- c(dif_amount, "Mostly negative")
        } else {
          if(!((abs(dif_amount[3]+.00001) / abs(dif_amount[1]+.00001) > 3) | (abs(dif_amount[1]+.00001) / abs(dif_amount[3]+.00001) > 3))){
            dif_amount <- c(dif_amount, "Other")
          }
        }
      }
    }
    c(names(thisvar)[1], out, dif_amount)
  })
}

@@

```{r}
if(run_everything){
  set.seed(34)
  p <- PartialDependence(x = final, vars = ordered_vars, output = "list", rawdata = TRUE)
  saveRDS(p, "p_train.RData")
  #source("../get_signs.R")

}
p <- readRDS("p_train.RData")
the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

@@

The definitive analysis was performed by applying to the whole data set the method that was found the most accurate, in this case MetaForest.

```{r}
set.seed(684842)
mf_full <- MetaForest(as.formula(paste0("yi~", paste0(ordered_vars, collapse = " + "))),
                      data = dat,
                      whichweights = "unif",
                      mtry = 3,
                      min.node.size = 2,
                      num.trees = 10000)

if(run_everything){
  set.seed(34)
  p <- PartialDependence(x = mf_full, vars = ordered_vars, output = "list", rawdata = TRUE)
  saveRDS(p, "p_full.RData")
}
p <- readRDS("p_full.RData")

the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

p_pdp <- metaforest:::merge_plots(p)
ggsave(
  filename = "rf_pdp_numbered_fulldata.png",
  p_pdp,
  device = "png")
svg("rf_pdp_numbered_fulldata.svg")
eval(p_pdp)
dev.off()

dirs <- data.frame(the_signs)
VI <- sort(mf_full$forest$variable.importance, decreasing = TRUE)
VI <- data.frame(Variable = paste0(1:length(VI), ". ", names(VI)), Importance = VI, Direction = dirs$V9[match(names(VI), dirs$V1)])
VI$Variable <- ordered(VI$Variable, levels = rev(VI$Variable))
VI$Direction <- ordered(VI$Direction, levels = c("Positive monotonous", "Mostly positive", "Other", "Mostly negative", "Negative monotonous"))

p_vi <- ggplot(VI, aes_string(y = "Variable", x = "Importance")) + 
  geom_segment(aes_string(x = 0, xend = "Importance", 
                          y = "Variable", yend = "Variable"), colour = "grey50", 
               linetype = 2) +
  geom_vline(xintercept = 0, colour = "grey50", 
             linetype = 1) +
  xlab("Permutation Importance") + 
  theme_bw() + theme(panel.grid.major.x = element_blank(), 
                     panel.grid.minor.x = element_blank(),
                     axis.title.y = element_blank(),
                     axis.text.y = element_text(hjust=0)) + 
  geom_point(aes_string(fill = "Direction"), shape = 21, size = 2) + 
  scale_fill_grey(start = 1, end =0) +
  #scale_fill_manual(values = c("Mostly positive" = "white", "Mostly negative" = "gray80", "Negative" = "black", "Other" = "gray50")) + 
  theme(legend.position = c(0.8, 0.2))
ggsave(
  filename = "varimp_fulldata.png",
  p_vi,
  device = "png")
svg("varimp_fulldata.svg")
eval(p_vi)
dev.off()

imp_p <- ranger::importance_pvalues(mf_full$forest, formula = yi ~., data = mf_full$data, method = "altmann")
VI$pvalue <- imp_p[,2][match(rownames(VI), rownames(imp_p))]
write.csv(VI, "table4_fulldata.csv", row.names = FALSE)
```
